---
title: "Project 2"
author: ''
date: "11/2/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load the required libraries
library(EBImage)
library(readxl)
library(tidyverse)
library(caret)
library(nnet)
library (randomForest)
library(e1071)
```

```{r}

# set working directory: Set this as the directory where you have your .rmd file and the "Data" folder
Wd_path="C:/Users/tpr16/OneDrive/Desktop/3rd sem/557 Data Mining I/project 2"
setwd(Wd_path)

# Read the excel file as data frame. Make sure to save the file as .xlsx instead of the default .csv extension
# class labels for all images
df = read_excel("./Data/ISIC_2019_Training_GroundTruth.xlsx",col_names=TRUE)
dim(df)
head(df)

```

```{r}

# The types of skin Lesion (8 types), Unknown is not considered as none of the labels corresponds to unknown   
Types = colnames(df)[2:9]    


w = 36    # Width of the image
h = 48   # Height of the image
N_features = w*h*3 # number of features



# matrix to store features, one image per row
features <- data.frame(matrix(0, nrow = dim(df)[1], ncol= (N_features+1) ))
row.names(features) <- df$image

# last column is the class label
colnames(features)[N_features+1] <- "type" 



f = matrix(0, nrow = 1, ncol=N_features)   # Empty row vector to store the unrolled pixel intensity data 
dim(f)



# Read the images based on type of Lesion, resize and assign to the corresponding column in the data frame
for (i in 1:length(Types)) {
  
   t=Types[i]     # Type of the Leasion
   lst=df$image[df[t]==1]    # Indexes of all images belonging to that leasion type
      
   # Read all images of a particular type
   for (j in 1:length(lst)){
        Name_I=lst[j]  # Name of the image
        pth=paste("Data/",t,"/",Name_I,".jpg",sep="")    #Path where image belong based on the name and type
        I = readImage(pth)     # Reading the image
        I_resized = resize(I,w,h)    # Resize into w*h
        f=t(as.vector(I_resized))       # Unroll the image. This unrolls column wise, picks 2nd column of red, places it below 1st, repets for R,G, and B
        features[Name_I,1:N_features]=f[1,1:N_features]
        features[Name_I,"type"]=t
   }
   
 }
save(features,file =paste(Wd_path,"/features.Rdata",sep=""))
```

In each row, we have 5185 features corresponding to one image.
* cells 1 to 36*48 (= 1728) for corresponding to red
* cells 1729 to 3456 corresponding to blue
* cells 3457 to 5184 corresponding to green

Last column of matrix corresponds to Lesion type
```{r}
load(file =paste(Wd_path,"/features.Rdata",sep=""))
dim(features)
features[1,1:100]

features$type = as.factor(features$type)
round(table(features$type)/sum(table(features$type)), 4)


```

# Divide into Testing and training sets
```{r}

test_size = round(0.75*dim(features)[1],0)
set.seed(1)
sample_points <- sample(1:nrow(features), test_size)

training.samples = features[sample_points,]
dim(training.samples)
# proportion of each type of images
sort(round(table(training.samples$type)/sum(table(training.samples$type)), 4))


testing.samples = features[-sample_points,]
dim(testing.samples)
```

# EDA

Average pixel intensities by "type"
What other EDA?
```{r}

Avg_intensities = aggregate(training.samples[,1:(dim(training.samples)[2]-1)], list(training.samples$type), mean)
dim(Avg_intensities)

RBG = factor(c(rep(1,w*h), rep(3,w*h), rep(2,w*h)))
length(RBG)
Avg_int_transpose = t(Avg_intensities[,2:5185])
colnames(Avg_int_transpose) = as.character(Avg_intensities[,1])
data.frame(Avg_int_transpose)

# i for red, 3 for blue; 2 for green
Avg_int_transpose = data.frame(cbind(Avg_int_transpose,RBG))
dim(Avg_int_transpose)


library(data.table)
# convert data to long form
Avg_int_transpose2 = melt(Avg_int_transpose, id.vars = c("RBG"), measure.vars = c("AK", "BCC", "BKL", "DF", "MEL", "NV", "SCC", "VASC"))
dim(Avg_int_transpose2)
head(Avg_int_transpose2)
colnames(Avg_int_transpose2)[2] = "type"


library(ggplot2)
library(dplyr)

 Avg_int_transpose2$RBG = as.factor(Avg_int_transpose2$RBG)
 Avg_int_transpose2 %>%
    ggplot(aes(value, fill = RBG)) + geom_histogram() + facet_wrap(~type) +
   xlab("Pixel Intensity") + ylab("Frequency")


    
```





# Dimension reduction using PCA
Summary - Based on both Kaiser's rule and examination of scree plot, we believe that retaining 15 PCs is good enough.
```{r}

# no scaling needed since all intensities lie between 0 and 1
pr.out <- prcomp(training.samples[,-ncol(training.samples)])
save(pr.out,file =paste(Wd_path,"/pca.Rdata",sep=""))
load(file =paste(Wd_path,"/pca.Rdata",sep=""))

#prop of variance explained by each PC
pr.var <- pr.out$sdev^2
prop_var <- pr.var / sum(pr.var)
prop_var[1:15]


cumsum(prop_var)[96]

# plot of cum. prop. of variance explained
plot(cumsum(prop_var), xlab = "Principal Component",
    ylab = "Cumulative Proportion of Variance Explained",
    ylim = c(0, 1), type = "p")
abline(h=0.96, v = 90,  col = "red")


# close up: First 10 PCs explain more than 80% variance in data
plot(cumsum(prop_var)[1:10], xlab = "Principal Component",
    ylab = "Cumulative Proportion of Variance Explained", xlim = c(0,10),
    ylim = c(0, 1), type = "p")
abline(h = 0.8, col = "red")


# 15 PCs explain 90% variation
plot(cumsum(prop_var)[1:50], xlab = "Number of principal Components",
    ylab = "Cumulative Proportion of Variance Explained", xlim = c(1,50),
    ylim = c(0, 1), type = "p")
abline(h = 0.9, v = 15, col = "red")


# 90 PCs explain 96% variation
plot(c(80:150),cumsum(prop_var)[80:150], xlab = "Number of principal Components",
    ylab = "Cumulative Proportion of Variance Explained", type = "p")
abline(h=0.96, v = 90,  col = "red")




# Kaiser's rule
pr.var[pr.var>=1]
length(pr.var[pr.var>=1])
```


# Rotated co-ordinates (restricted to 15 PCs)
```{r}

# reference: https://hastie.su.domains/ISLR2/Labs/Rmarkdown_Notebooks/Ch12-unsup-lab.html


dim(pr.out$rotation)

fifteen_PCs = as.matrix(pr.out$rotation[,1:15])
sum(fifteen_PCs[,1]^2) # adds to 1 as expected

# reduced dimension after projecting data onto first 15 PCs
train_red_features = as.matrix(training.samples[,-ncol(training.samples)]) %*% fifteen_PCs
dim(train_red_features)

train_red_features = data.frame(train_red_features)
head(train_red_features)

save(train_red_features,file =paste(Wd_path,"/reduced_features.Rdata",sep=""))
load(file =paste(Wd_path,"/reduced_features.Rdata",sep=""))
```


# Interpreting PCs


score plots - no visible clustering observed in the
```{r}
# reference:  https://www.geo.fu-berlin.de/en/v/soga/Geodata-analysis/Principal-Component-Analysis/principal-components-basics/Derive-synthetic-variables/index.html

Z = train_red_features[,1:4]
names(Z)
head(Z)

Z1 = cbind(Z,training.samples[,ncol(training.samples)]) 
dim(Z1)
colnames(Z1)[dim(Z1)[2]] = "type"
Z1$type = factor(Z1$type)
head(Z1)

# no visible clustering
Z1 %>%
    ggplot(aes(PC1, PC2, col = type)) + geom_point()  # + facet_wrap(~type)


#### extra ############################ 

Z1 %>%
    ggplot(aes(PC1, PC2)) + geom_point() 


plot(Z[,1:2], xlab = 'Data projected along PC1', ylab = 'Data projected along PC2')
abline(h = mean(Z[,1]), col = "blue")
abline(v = mean(Z[,2]), col = "green")

```

Loading plot
```{r}


```

Other PCA interpretatons, if possible
```{}

```


Dimension reduction on test data
```{r}
pr.out.test = prcomp(testing.samples[,-ncol(testing.samples)])
save(pr.out.test,file = paste(Wd_path,"/test_reduced.Rdata", sep="" ))
load(file = paste(Wd_path,"/test_reduced.Rdata", sep="" ))


Z2 = pr.out.test$rotation # matrix of PCs
fifteen_PCs_test = as.matrix(Z2[,1:15])
dim(Z2)
sum(fifteen_PCs_test[,1]^2) # sum is one as expected


test_red_features = as.matrix(testing.samples[,-ncol(testing.samples)]) %*% fifteen_PCs_test
dim(test_red_features)


class(testing.samples[,ncol(testing.samples)])
test_labels = testing.samples[,ncol(testing.samples)] 
test_labels = factor(test_labels)
head(test_labels)
```

# Tree based methods


Single tree:
Classifies into three most prevalent categories. Problems:
1) imbalanced data
2) too many categories and we are using information gain
```{r}

# reference: https://rstudio-pubs-static.s3.amazonaws.com/222569_a8d12e00f8204a479e84a33b49e54790.html
# https://stat.ethz.ch/R-manual/R-devel/library/rpart/html/rpart.control.html



library(rpart)
library(rpart.plot)

head(train_red_features)
type = factor(training.samples[,ncol(training.samples)])
train_red_features = cbind(train_red_features, type)
head(train_red_features)

# inbuilt rpart stopping rules are only able to classifiy into three classes
# inbuilt rpart stopping criteria  : rpart.control(minsplit = 20, minbucket = round(minsplit/3), cp = 0.01, 
      #                              maxcompete = 4, maxsurrogate = 5, usesurrogate = 2, xval = 10,
      #                              surrogatestyle = 0, maxdepth = 30, ...)

head(train_red_features)

tree.lesion.std = rpart(train_red_features$type ~ ., train_red_features[,-ncol(train_red_features)], method = "class", parms = list(split = 'information'))
rpart.plot(tree.lesion.std)
printcp(tree.lesion.std)

# we observe that the three most prevalent classes BCC, MEL and NV only are the classification categories in the tree
sort(round(table(training.samples$type)/sum(table(training.samples$type)), 4))


level = levels(training.samples$type)

tree.test = predict(tree.lesion.std, data.frame(test_red_features))

tree.pred = matrix(0, nrow = dim(tree.test)[1], ncol = 1)

for (j in 1:dim(tree.test)[1]) {
 
  index = which.max(tree.test[j,])
   tree.pred[j,1] = level[index]
}

tree.pred= factor(tree.pred)

# 51.5%
conf.matrix.tree = table(tree.pred, test_labels)
conf.matrix.tree
(239+3025)/dim(tree.test)[1]


####################################################################################################

# cp is the complexity parameter C_alpha(T) = C(T) + alpha* |T|
# Small α results in larger trees and potential overfitting
another_tree = rpart(training.samples$type ~ ., train_red_features,control = rpart.control(cp = 0.002), method = "class", parms = list(split = 'information'))
bestcp <- tree.lesion.std$cptable[which.min(tree.lesion.std$cptable[,"xerror"]),"CP"]

tree.pruned <- prune(tree.lesion.std, cp = bestcp)
rpart.plot(tree.pruned)


test_red_features
tree.lesion = rpart(training.samples$type ~ ., train_red_features, method = "class", control = rpart.control(minsplit = 10, cp = 0.002))
rpart.plot(tree.lesion)
tree.lesion




```


Tree using information gain - C5.0
The model fit is called C5.0 (which is an upgrade of C4.5)
This model solves the problem of too many categories to some extent - has 6 categories, misses two less prevelant
Data still imbalanced - so low accuracy
```{r}
library(C50)
library(printr)

# https://rpubs.com/kjmazidi/195428


# someimproved - classified into 6 classes
# categories not present in tree - DF, SCC (least, third from last in amount of samples)
C5.0_tree_train = C5.0(train_red_features$type~., data = train_red_features ) 
summary(C5.0_tree_train)
plot(C5.0_tree_train)
text()




### Applying on test set
class(test_red_features)
test_red_features = data.frame(test_red_features)
head(test_red_features)

test_pred_C5.0 <- predict(object=C5.0_tree_train, newdata=test_red_features, type="class")
# plot(C5.0_tree_train) # runs for too long


conf.matrix = table(test_pred_C5.0, test_labels)
conf.matrix[1,1]

sum = 0
for (t in 1:8) {
  
  sum = sum + conf.matrix[t,t]
}

sum


# we observe only 43% classification accuracy (Since data imbalance not addressed yet)
sum/dim(test_red_features)[1]



```

# Bagging
Since PCs are uncorrelated, the trees fit for different bootstrap samples do not exhibit excessive variation. But weak learners are not independent as we have "strong predictors"

We observe 63\% classification accuracy. The most well classified is the class NV (which is most in proportion). Classification error is closest to 1 in case of classes that are less in proportion. Under representation of less prop classes in bootstrap samples.

Most classified as the two major categories - problem: imbalanced data
```{r}
set.seed(1)
bag.train.tree = randomForest(train_red_features$type~., data = train_red_features, mtry = 15, importance = T)
bag.train.tree

bag.conf = bag.train.tree$confusion
sort(bag.conf[,9]) # classification error for each class



# Applying on test set

bag.test = predict(bag.train.tree, test_red_features)

conf.matrix.bag = table(bag.test, test_labels)
conf.matrix.bag

sum.bag = 0
for (t in 1:8) {
  
  sum.bag = sum.bag + conf.matrix.bag[t,t]
}

# 36% accuracy
sum.bag/dim(test_red_features)[1]
```


# Random forest classifier
Clearly, PC1 is a more important variable. Therefore bagging would not involve independent trees. RF classifier will help de-correlate the tree topologies.

Most classified into two major categories: problem = imbalanced data
```{r} 
rf.train = randomForest(train_red_features$type~., data = train_red_features, importance = TRUE)
rf.train

# applying on test data
rf.test = predict(rf.train, test_red_features)

conf.matrix.rf = table(rf.test, test_labels)
conf.matrix.rf

sum.rf = 0
for (t in 1:8) {
  
  sum.rf = sum.rf + conf.matrix.rf[t,t]
}

# 39% accuracy
sum.rf/dim(test_red_features)[1]
```

# Boosting

Is there a multi class huber loss?
```{r}
library(caret)
library(gbm)

# ref: https://rpubs.com/nkrohrmann/predictionclasse


class(train_red_features$type)
boost.train = gbm(train_red_features$type~., data = train_red_features, distribution = "multinomial", n.trees = 500)
summary(boost.train)

boost.train.5 = gbm(train_red_features$type~., data = train_red_features, distribution = "multinomial", n.trees = 5)

# apply on test data


test_red_features = data.frame(test_red_features)
#  the prediction it produced was a data frame that contained the likelihood of each level of the factor variable classe for every entry.
boost.test = predict(boost.train, test_red_features)
boost.test.5 = predict(boost.train.5, test_red_features)


# I used the for loop below to determine the most likely classe respectively and store it in a new data frame
boost.test <- as.data.frame(boost.test)
boost.test.5 <- as.data.frame(boost.test.5)
dim(boost.test)


level = levels(training.samples$type)

boost.pred.5 = matrix(0, nrow = dim(boost.test.5)[1], ncol = 1)
dim(boost.test.5)[1] # somehow 3D array with third co-ord = 1


for (j in 1:dim(boost.test.5)[1]) {
 
  index = which.max(boost.test.5[j,,1])
   boost.pred.5[j,1] = level[index]
}

boost.pred= factor(boost.pred.5)

conf.matrix.boost = table(boost.pred, test_labels)
conf.matrix.boost


# 48% for 5 trees boosting
(2652+427)/dim(boost.test.5)[1]

# 29% for 200 trees
 (1034+784)/dim(boost.test)[1]


# 26% accuracy for 100 trees
(1071+563)/dim(boost.test)[1]

# 23% for 500 trees
 (1082+ 401)/dim(boost.test)[1]
```
Possible improvement: starting weight is a prior density that incorporates imbalance in data


# SVM
How to pick kernel?
```{r}

svm.train = svm(train_red_features$type ~ ., data = train_red_features, kernel = "linear", gamma = 0.1, cost = 10)

svm.test = predict(svm.train, test_red_features)

conf.matrix.svm.linear = table(svm.test, test_labels)

(69+3162)/dim(test_red_features)[1]



svm.train = svm(train_red_features$type ~ ., data = train_red_features, kernel = "radial", gamma = 5, cost = 10)

svm.test = predict(svm.train, test_red_features)

conf.matrix.svm.radial = table(svm.test, test_labels)

(69+3162)/dim(test_red_features)[1]




summary(svm.train)
svm.train$decision.values
svm.test = as.factor(svm.test)


set.seed(1)
tune.out <- tune(svm, train_red_features$type ~ ., data = train_red_features, 
    kernel = "linear", 
    ranges = list(
      cost = c(0.1, 1, 10, 20, 100),
      gamma = c(0.5, 1, 2, 3, 4)
    )
  )
summary(tune.out)

```

# Dealing with imbalenced data: Downsampling with SMOTE
```{r}
# reference: https://topepo.github.io/caret/subsampling-for-class-imbalances.html
# https://www.rdocumentation.org/packages/caret/versions/6.0-92/topics/trainControl

library(smotefamily)

smote_train = SMOTE(train_red_features[,-ncol(train_red_features)], train_red_features$type)
dim(smote_train$data)
smote_syn_data = smote_train$data


names(smote_syn_data)[ncol(smote_syn_data)] = "type"
smote_syn_data$type = factor(smote_syn_data$type)

save(smote_syn_data,file = paste(Wd_path,"/smote_train.Rdata", sep="" ))
load(file = paste(Wd_path,"/smote_train.Rdata", sep="" ))

smote_prop_train = round(prop.table(table(smote_syn_data$type)),4)

orig_prop_train = round(table(training.samples$type)/sum(table(training.samples$type)), 4)

orig_prop_train; smote_prop_train 

```

# Applying classification algorithms on synthetic data
boosted C5.0 - if too many bagging iterations then performance gets worse due to too many outliers.
bagged SVM - couldn't do
svm on smote data
bagged C5.0
RF on C.5 
logistic
```{r}
library(caret)
library(C50)
library(kernlab)


# smote_C5.0 = train(smote_syn_data$type~., data = smote_syn_data, method = "C5.0")
# smote_rf_train = train(smote_syn_data$type~., data = smote_syn_data, method = "rf", trControl = ctrl)

bagctrl = bagControl(fit = svmBag$fit, predict = svmBag$pred, aggregate = svmBag$aggregate)
ctrl = trainControl(method = "cv", number = 5)


# Random Forest
smote_rf_train = randomForest(smote_syn_data$type~., data = smote_syn_data, ntree = 100)
save(smote_rf_train,file =paste(Wd_path,"/smote_rf_100trees.Rdata",sep=""))
load(file = paste(Wd_path,"/smote_rf_100trees.Rdata", sep="" ))


# C5.0
smote_C5.0_1 =  C5.0(smote_syn_data[,-ncol(smote_syn_data)], smote_syn_data$type, trials = 1)

# Boosted C50
smote_C5.0 =  C5.0(smote_syn_data[,-ncol(smote_syn_data)], smote_syn_data$type, trials = 5)
save(smote_C5.0,file =paste(Wd_path,"/smote_C5.0_5trials.Rdata",sep=""))
load(file = paste(Wd_path,"/smote_C5.0_5trials.Rdata", sep="" ))


smote_C5.0_10 =  C5.0(smote_syn_data[,-ncol(smote_syn_data)], smote_syn_data$type, trials = 10)

smote_C5.0_50 =  C5.0(smote_syn_data[,-ncol(smote_syn_data)], smote_syn_data$type, trials = 50)


# Bagged SVM - keep getting error
svmbag <- train(smote_syn_data$type~., data = smote_syn_data, "bag", bagControl = bagctrl)


# methods
smote_rf_train
smote_C5.0$boostResults
smote_C5.0_50$boostResults

smote_rf_train
smote_rf_train$forest


# svm on smote data - what else is the problem?

svm.train.smote = svm(smote_syn_data$type ~ ., data = smote_syn_data, kernel = "linear", gamma = 0.1, cost = 10)
save(svm.train.smote,file =paste(Wd_path,"/smote_svm.Rdata",sep=""))
load(file = paste(Wd_path,"/smote_svm.Rdata", sep="" ))


svm.test.smote = predict(svm.train.smote, test_red_features)

conf.matrix.svm.smote = table(svm.test.smote, test_labels)

(69+3162)/dim(smote_syn_data)[1]



svm.train = svm(train_red_features$type ~ ., data = train_red_features, kernel = "radial", gamma = 5, cost = 10)

svm.test = predict(svm.train, test_red_features)

conf.matrix.svm = table(svm.test, test_labels)

(69+3162)/dim(test_red_features)[1]



# predictions
smote_C5.0_1_pred = predict(smote_C5.0_1, test_red_features)
sum(diag(table(smote_C5.0_1_pred, test_labels)))/length(test_labels)

smote_C5.0_pred = predict(smote_C5.0, test_red_features)
table(smote_C5.0_pred, test_labels)
sum(diag(table(smote_C5.0_pred, test_labels)))/length(test_labels) # 39% accuracy for just 5 trees


smote_C5.0_10_pred = predict(smote_C5.0_10, test_red_features)
table(smote_C5.0_10_pred, test_labels)
sum(diag(table(smote_C5.0_10_pred, test_labels)))/length(test_labels)



# same issue of MEL, NV
smote_C5.0_50_pred = predict(smote_C5.0_50, test_red_features)
table(smote_C5.0_50_pred, test_labels)
sum(diag(table(smote_C5.0_pred, test_labels)))/length(test_labels)


smote_rf_ptrd = predict(smote_rf_train, test_red_features)
table(smote_rf_ptrd, test_labels)
```



# bagging C5.0 on smote
```{r}

library(baguette)
C5.0_bag_smote = bagger(smote_syn_data[,-ncol(smote_syn_data)], smote_syn_data$type, base_model = "C5.0", times = 100 )

class(test_labels)
length(test_labels)



C5.0_bag_smote_pred = predict(C5.0_bag_smote, test_red_features)
class(C5.0_bag_smote_pred)
colnames(C5.0_bag_smote_pred) = "type"
dim(C5.0_bag_smote_pred)

is.na(as.numeric(C5.0_bag_smote_pred[1,1]) == as.numeric(test_labels[1]) )

tot = 0

for (j in 1:dim(C5.0_bag_smote_pred)[1]) {

  if (as.numeric(C5.0_bag_smote_pred[j,1])==as.numeric(test_labels[j])){
    tot = tot + 1
  }
    
}

tot # 2726
tot/dim(test_red_features)[1]


```








# Dimension reduction using neural networks
```{r}
view(USArrests)

```
























```{r}

df_subset=df[1:6500,]
set.seed(1)
training.samples <- df_subset$type %>% createDataPartition(p = 0.75, list = FALSE)
train.data  <- df_subset[training.samples, ]
test.data <- df_subset[-training.samples, ]
```

```{r}
# Logistic Regression
start_time <- Sys.time()
logistic <- nnet::multinom(type ~., data = train.data)
# Summarize the model
summary(logistic)
# Make predictions
predicted.classes <- logistic %>% predict(test.data)
end_time <- Sys.time()
logistic_time=end_time - start_time
head(predicted.classes)
# Model accuracy
mean(predicted.classes == test.data$type)
```

```{r}
# RandomForest
start_time <- Sys.time()
RF=randomForest(type~., data = train.data )
# Summarize the model
summary(RF)
# Make predictions
predicted.classes <- RF %>% predict(test.data)
end_time <- Sys.time()
logistic_time=end_time - start_time
head(predicted.classes)
# Model accuracy
mean(predicted.classes == test.data$type)
```

```{r}
#Support Vector Machine
start_time <- Sys.time()
svm = svm(type~. , data = train.data, kernel = "radial", cost = 10, scale = FALSE)
# Summarize the model
summary(svm)
# Make predictions
predicted.classes <- svm %>% predict(test.data)
end_time <- Sys.time()
logistic_time=end_time - start_time
head(predicted.classes)
# Model accuracy
mean(predicted.classes == test.data$type)
```

```{r}




for (i in dim(boost.test)[1]){
  
  max <- max(boost.test[i,])
  
  if(boost.test[i,1] == max){
    
    de <- "AK"
    df <- rbind(df, de)
    }
  else if(boost.test[i,2] == max){
    
    de <- "BCC"
    df <- rbind(df, de)
    }
  else if (boost.test[i,3] == max){
    
    de <- "BKL"
    df <- rbind(df, de)
    }
  else if (boost.test[i,4] == max){
    
    de <- "DF"
    df <- rbind(df, de)
  }
  else if (boost.test[i,5] == max){
    
    de <- "MEL"
    df <- rbind(df, de)
  }
  else if (boost.test[i,6] == max){
    
    de <- "NV"
    df <- rbind(df, de)
  }
    else if (boost.test[i,7] == max){
    
    de <- "SCC"
    df <- rbind(df, de)
  }
  else {
    de <- "VASC"
    df <- rbind(df, de)
  }
  
  
}

```

```{r}
library(caret)
# https://topepo.github.io/caret/subsampling-for-class-imbalances.html
set.seed(3)

down_train = downSample(train_red_features, train_red_features$type)

down_train
table(train_red_features$type)
table(down_train$type)

# too few in each sample



library(smotefamily)
set.seed(4)
smote_train = SMOTE( train_red_features[,-dim(train_red_features)[2]], train_red_features$type )
class(smote_train)


# A resulting dataset consists of original minority instances, synthetic minority instances and original majority instances 
down_train1 = smote_train$data
dim(down_train1[,-16])
dim(train_red_features[,-16])
dim(down_train[,-c(16,17)]) # one extra type column attached
# again imbalanced



round(table(training.samples$type)/sum(table(training.samples$type)), 4)
round(prop.table(table(down_train1$class)),4)
prop.table(table(down_train$type))


table(training.samples$type)
table(down_train1$class)
table(down_train$type)


library(ROSE)
set.seed(9560)
rose_train <- ROSE(train_red_features$type ~ ., data = train_red_features)$data       



```



# Applying classification algorithms on down_train1
```{r}
names(down_train1)[16] = "type"
down_train1$type = factor(down_train1$type)
C5.0_down_train1 = C5.0(down_train1$type~., data = down_train1 ) 




test_pred_down_C5.0 <- predict(object=C5.0_down_train1, newdata=test_red_features, type="class")
# plot(C5.0_tree_train) # runs for too long


conf.matrix.down1 = table(test_pred_down_C5.0, test_labels)
conf.matrix[1,1]

sum1 = 0
for (t in 1:8) {
  
  sum1 = sum1 + conf.matrix.down1[t,t]
}


```



```{r}


```
